M-M paper, morphological dependence

### 2015-04-02 papers/MbhMsph/mm.tex
c

\title{M-M paper, morphological bias }

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

@@

\begin{abstract}
abstract 
\end{abstract}

@@

\begin{table*}
\centering
\caption{Linear regression analysis.}
\begin{tabular}{llccccc}
\hline
\hline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\hline 
\\
 & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\ 
                   & BCES OLS$(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
                   & FITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
                   & FITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
                   & FITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\

@@

Late-type (S) (17) & BCES OLS$(Y|X)$   & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
 		   & BCES OLS$(X|Y)$   & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
 		   & BCES Bisector     & $7.2 \pm 0.2$ & $-1.1 \pm 0.3$ & $-22.33$ & $-$    & $0.88$ \\
 		   & FITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
 		   & FITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
 		   & FITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
\hline 
\\
 & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $$ & $-$ & $0.4487$ \\
 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $$ & $-$ & $0.5329$ \\
 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $$ & $-$ & $0.4713$ \\
 		       & FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
 		       & FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
 		       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\

>>>>

\title{M-M paper, morphological dependence }

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1} and A. Marconi and E. Sani and L.K. Hunt}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

@@

\begin{abstract}
We have the best latest M-L and M-M diagrams (66 galaxies = biggest sample ever used, IR imaging = minimally affected by dust and star formation, 
state-of-the-art multicomponent galaxy decompositions = 
we fit bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores).
Previous samples were overwhelmingly dominated by early-type galaxies, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7 M_\odot$,
thus we can explore the low-mass end of the diagrams.
We provide a table with spheroid luminosities, spheroid stellar masses and galaxy luminosities. 
We give updated linear regressions for Sersic/core-Sersic galaxies and for different morphological types (E/S0, Sp). 
Sersic and core-Sersic galaxies have slopes consistent with each other (contrary to what claimed by GS13). 
In the M-M diagram, bulges of early type galaxies have a slope of $\sim$1, while bulges of spiral galaxies have a slope of 2-3.
Linear regressions that we provide are symmetrical (to be compared with theoretical expectations) and non-symmetrical (to be used to predict BH masses).
Contrary to a previous claim, the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.
Bulges with $n<2$, claimed by some to be pseudobulges, are not offset to lower BH masses from the correlation defined by bulges with $n>2$.

\end{abstract}

@@

\begin{table*}
\centering
\caption{Linear regression analysis.}
\begin{tabular}{llccccc}
\hline
\hline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\hline 
\\
 & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
All (66)	       & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
		       & BCES OLS$(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
		       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
		       & FITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
		       & FITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
		       & FITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\

Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\ 
                   & BCES OLS$(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
                   & FITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
                   & FITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
                   & FITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\

@@

Late-type (S) (17) & BCES OLS$(Y|X)$   & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
 		   & BCES OLS$(X|Y)$   & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
 		   & BCES Bisector     & $7.2 \pm 0.2$ & $-1.1 \pm 0.3$ & $-22.33$ & $-$    & $0.88$ \\
 		   & FITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
 		   & FITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
 		   & FITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
\hline 
\\
 & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
 		       & BCES OLS$(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
 		       & BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
 		       & FITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
 		       & FITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
 		       & FITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\

Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
 		       & FITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
 		       & FITEXY OLS$(X|Y)$ & $8.56^{+0.07}_{-0.09}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.79$ & $0.55$ \\
 		       & FITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\

%All (62)		& BCES OLS$(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
%			& BCES OLS$(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
%			& BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
%			& FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
%			& FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
%			& FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
